Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-06-27 analysis/paper/paper.Rmd

```{r plot-all-spatial-pattern, fig.cap= "Spatial pattern of ornaments"}
ggplot(ornaments_period_join) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join, aes(fill =n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
```

@@

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Golden Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Glass Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Agate Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_metal) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_metal, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Metal Ring",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_bell) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_bell, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Copper Bell",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
```

>>>>

```{r plot-all-spatial-pattern, fig.cap= "Spatial pattern of ornaments"}
ggplot() +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join, 
          aes(geometry = geometry, 
              fill =n), 
          alpha = 0.9) +
  facet_wrap(~ period) +
  labs(fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
```

@@

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, 
          aes(geometry = geometry,
              fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Golden Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, 
          aes(geometry = geometry,
              fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Glass Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, 
          aes(geometry = geometry, 
              fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Agate Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_metal) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_metal, 
          aes(geometry = geometry,
              fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Metal Ring",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

@@

# plot by period
ggplot(ornaments_period_join_bell) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_bell, 
          aes(geometry = geometry,
              fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Copper Bell",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
```
